{\bf \huge Wikiplia}:\\ The Free Programming Language\\ That Anyone Can Edit

### 2007-06-11 trunk/wikiplia/paper/wikiplia.tex
typo

\newcommand\currentrevision{532}
\newcommand\currentsizekb{250}
\newcommand\wikipliaurl{http://wikiplia.spacebar.org/}

@@

The remainder of this paper proceeds as follows. We first present in
Section~\ref{sec:calculus} the design of the initial Wikiplia system,
which is used to bootstrap the rest of Wikiplia. We then discuss the
current state of Wikiplia as of revision \currentrevision\ in
Section~\ref{sec:current}. We explain the freedom-preserving TIA
Public License in Section~\ref{sec:license}. We conclude with a
discussion of unrelated work and plans for the future~\ref{sec:conc}.

@@

All popular modern languages are defined via a definitional
interpreter\wcite{JavaScript}$^,$\wcite{Objective
Caml}$^,$\wcite{Perl} with accompanying O'Reilly ``animal''
book.\z\wcite{O'Reilly Media} The work on Wikiplia is unrelated: We
have no animal mascot\wcite{ORLY owl} and the languages are described
by a tower of source-to-source translations on top of a universally
parseable semantic document in XML\wciteshort{Category:ML programming
language family} form.

The author doesn't think\wcite{Thought} much of
musicals,\z\wcite{Musical theatre} to be perfectly\wcite{Thomas
Aquinas} honest,\z\wcite{Honesty} so those are basically\wcite{BASIC}
a no-go. He also feels that the metric system\wcite{Metric system} but
paradoxically\wcite{Pardadox} also time zones\wcite{Time zone} are
pretty overrated. Ketchup\wcite{Ketchup} on eggs\wcite{Egg (food)} is
gross,\z\wcite{Gross} but not quite as gross as foie gras\wcite{Foie
gras}, which more or less has the word\wcite{Word} ``gross'' in its
name\wcite{Name} so duh.\z\wcite{Duh}

>>>>

\newcommand\currentrevision{532}
\newcommand\currentsizekb{250}
\newcommand\wikipliaurl{http://wikiplia.spacebar.org:2222/}

@@

The remainder of this paper proceeds as follows. We first present in
Section~\ref{sec:calculus} the design of the initial Wikiplia system,
which is used to bootstrap the rest of Wikiplia. We then discuss the
current state of Wikiplia as of revision \currentrevision\ in
Section~\ref{sec:current}. We explain the freedom-preserving TIA
Public License in Section~\ref{sec:license}. We conclude with a
discussion of unrelated work and plans for the future in
Section~\ref{sec:conc}.

@@

All popular modern languages are defined via a definitional
interpreter\wcite{JavaScript}$^,$\wcite{Objective
Caml}$^,$\wcite{Perl} with accompanying O'Reilly ``animal''
book.\z\wcite{O'Reilly Media} The work on Wikiplia is unrelated: We
have no animal mascot\wcite{ORLY owl} and the languages are described
by a tower of source-to-source translations\wcite{Translation} on top
of a universally parseable semantic document in
XML\wciteshort{Category:ML programming language family} form.

The author\wcite{Author} doesn't think\wcite{Thought} much of
musicals,\z\wcite{Musical theatre} to be perfectly\wcite{Thomas
Aquinas} honest,\z\wcite{Honesty} so those are basically\wcite{BASIC}
a no-go. He also feels that the metric system\wcite{Metric system} but
paradoxically\wcite{Pardadox} also time zones\wcite{Time zone} are
pretty overrated. Ketchup\wcite{Ketchup} on eggs\wcite{Egg (food)} is
gross,\z\wcite{Gross} but not quite as gross as foie
gras,\z\wcite{Foie gras} which more or less has the word\wcite{Word}
``gross'' in its name\wcite{Name} so duh.\z\wcite{Duh}
